Developing a Visual Studio Code Language Support Extension for the Snail Programming Language

### 2023-06-19 paper.tex
backup

@@

\begin{figure}[b]
    \begin{subfigure}[c][][c]{0.45\textwidth}
        \includegraphics[width=\textwidth]{no-dap-theory.png}
        \caption{Communication between a generic debugger and a development tool is incredibly complicated.}
        \label{fig:no-dap-theory}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[c][][c]{0.45\textwidth}
        \includegraphics[width=\textwidth]{dap-theory.png}
        \caption{With the Debug Adapter Protocol, a development tool can easily communicate with a generic langauge-specific debugger.}
        \label{fig:dap-theory}
    \end{subfigure}
    \caption{Illustrating the benefit of the Debug Adapter Protocol in aiding development tool and debugger communication.}
    \label{fig:dap}
\end{figure}

@@

>>>>

\begin{figure}[h]
    \begin{subfigure}[c][][c]{0.45\textwidth}
        \includegraphics[width=\textwidth]{no-dap-theory.png}
        \caption{Communication between a generic debugger and a development tool is incredibly complicated.}
        \label{fig:no-dap-theory}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[c][][c]{0.45\textwidth}
        \includegraphics[width=\textwidth]{dap-theory.png}
        \caption{With the Debug Adapter Protocol, a development tool can easily communicate with a generic langauge-specific debugger.}
        \label{fig:dap-theory}
    \end{subfigure}
    \caption{Illustrating the benefit of the Debug Adapter Protocol in aiding development tool and debugger communication.}
    \label{fig:dap}
\end{figure}

@@

@@

Snail Language Support does not currently provide a debugger for the snail language. However, the extension is structured to support a snail debugger in the future.

\begin{itemize}
    \item defining a debug adapter for the extension
    \item defining a debug adapter inside of snail
    \begin{itemize}
        \item reasonML
        \item ocaml-dap
        \item lwt
    \end{itemize}
    \item initialization process of that debug adapter (incl. diagram)
    \item appendix of commands to implement in the future (incl. diagram)
\end{itemize}
